---
title: "Ski the DMV"
format: 
  html:
    page-layout: article
    toc: true
    toc-location: left
execute:
    echo: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

# Finding the right ski resort for my trip

If you're like me, you enjoy skiing and want a simple resource to figure out where to go if you live in the greater Washington, DC are. There are websites that describe the resorts, but I had a hard time finding one that put info about each one into a single table that I could search and filter to find the information that I want. So, I decided to solve my own problem and made this site. 

One of the more useful features that may be less obvious to new skiers is that this site provides information on the type of ski pass -- Epic or Ikon -- each resort uses. This saves me from having to check individual websites.

# Map of Ski Resorts within 5 Hours of DC

This interactive map shows ski resorts within a 5-hour drive of Washington, DC. **Hover over markers to see resort names**, click for detailed information, and add circle layers to show approximate driving distances for 2, 3, 4, and 5 hours from Washington, DC.

Each popup provides basic information about the ski resorts that you clicked on and a link to the resort's website. 

::: {.callout-note}
## About the Map

- **Map Style**: OpenFreeMap Liberty (OpenStreetMap-based)
- **Layer Control**: Click the layers icon (📋 top-left) to toggle drive time zones on/off
- **Drive Time Zones** (optional layers):
  - 🔵 2hr/100mi (blue) | 🟢 3hr/150mi (green) | 🟡 4hr/200mi (yellow) | 🔴 5hr/250mi (red)
  - Based on ~50mph average for mountainous/winding roads
  - Straight-line distances - actual routes follow roads
- **Hover over markers** to see resort names
- **Click markers** to see detailed information
- **Zoom in/out** - distance zones scale properly with geography
- **Marker colors**: Red (Epic) | Blue (Ikon) | Grey (Independent)
:::

```{r load-libraries}
library(tidyverse)
library(mapgl)
library(reactable)
library(reactablefmtr)
library(htmltools)
library(htmlwidgets)
library(sf)
```

```{r create-data}
#Compiled data on mid-Atlantic ski resorts within a 5 hour drive of Washington, DC
ski_resorts <- readxl::read_xlsx("ski_resort_data.xlsx") |> 
  mutate(
     # Convert float columns to integers
    beginner_pct = as.integer(beginner_pct),
    intermediate_pct = as.integer(intermediate_pct),
    advanced_pct = as.integer(advanced_pct),
    num_trails = as.integer(num_trails),
    terrain_acres = as.integer(terrain_acres),
    base_elevation = as.integer(base_elevation),
    peak_elevation = as.integer(peak_elevation),
    avg_snowfall = as.integer(avg_snowfall),
    vertical_drop = as.integer(vertical_drop),
    image_url = ifelse(
      !grepl("^https?://", image_url),  # If not already a full URL
      paste0("./", image_url),            # Add ./ prefix for relative path
      image_url               
  )

# Determine pass type color for each resort
ski_resorts <- ski_resorts %>%
  mutate(
    pass_color = case_when(
      pass_type == "Epic" ~ "#DC2626",
      pass_type == "Ikon" ~ "#0EA5E9",
      TRUE ~ "#808080"  # Grey for Independent
    ),
    # Create popup HTML for each resort
    popup_content = sprintf('
<div style="font-family: Arial, sans-serif; min-width: 220px; max-width: 260px;">
  <div style="display: flex; align-items: center; margin-bottom: 8px; padding-bottom: 6px; border-bottom: 2px solid #3b82f6;">
    <img src="%s" alt="%s" style="height: 24px; width: auto; margin-right: 8px; object-fit: contain;">
    <h3 style="margin: 0; color: #1e40af; font-size: 14px; font-weight: bold;">%s</h3>
  </div>
  <table style="width: 100%%; border-collapse: collapse; font-size: 11px;">
    <tr style="background-color: #f3f4f6;">
      <td style="padding: 4px; font-weight: bold; border: 1px solid #e5e7eb; width: 38%%;">Location</td>
      <td style="padding: 4px; border: 1px solid #e5e7eb;">%s, %s</td>
    </tr>
    <tr>
      <td style="padding: 4px; font-weight: bold; border: 1px solid #e5e7eb;">Pass</td>
      <td style="padding: 4px; border: 1px solid #e5e7eb;"><strong style="color: %s;">%s</strong></td>
    </tr>
    <tr style="background-color: #f3f4f6;">
      <td style="padding: 4px; font-weight: bold; border: 1px solid #e5e7eb;">Trails</td>
      <td style="padding: 4px; border: 1px solid #e5e7eb;">%d on %d acres</td>
    </tr>
    <tr>
      <td style="padding: 4px; font-weight: bold; border: 1px solid #e5e7eb;">Terrain Park</td>
      <td style="padding: 4px; border: 1px solid #e5e7eb;">%s</td>
    </tr>
    <tr style="background-color: #f3f4f6;">
      <td style="padding: 4px; font-weight: bold; border: 1px solid #e5e7eb;">Difficulty</td>
      <td style="padding: 4px; border: 1px solid #e5e7eb;">
        <span style="color: #22c55e;">●</span>%d%% <span style="color: #3b82f6;">■</span>%d%% <span style="color: #000;">◆</span>%d%%
      </td>
    </tr>
    <tr>
      <td style="padding: 4px; font-weight: bold; border: 1px solid #e5e7eb;">Elevations</td>
      <td style="padding: 4px; border: 1px solid #e5e7eb;">
        Base: %s ft. | Peak: %s ft. | Drop: %s ft.
      </td>
    </tr>
    <tr style="background-color: #f3f4f6;">
      <td style="padding: 4px; font-weight: bold; border: 1px solid #e5e7eb;">Snow</td>
      <td style="padding: 4px; border: 1px solid #e5e7eb;">%d in/yr</td>
    </tr>
    <tr>
      <td style="padding: 4px; font-weight: bold; border: 1px solid #e5e7eb;">Drive</td>
      <td style="padding: 4px; border: 1px solid #e5e7eb;">%.1f hrs</td>
    </tr>
    <tr style="background-color: #f3f4f6;">
      <td colspan="2" style="padding: 5px; text-align: center; border: 1px solid #e5e7eb;">
        <a href="%s" target="_blank" style="color: #2563eb; text-decoration: none; font-weight: bold; font-size: 10px;">
          🌐 Website
        </a>
      </td>
    </tr>
  </table>
</div>',
      image_url, name, name,
      city, state,
      pass_color, pass_type,
      num_trails, terrain_acres,
      terrain_park,
      beginner_pct, intermediate_pct, advanced_pct, 
      format(base_elevation, big.mark = ","),
      format(peak_elevation, big.mark = ","),
      format(vertical_drop, big.mark = ","),
      avg_snowfall,
      drive_time_hours,
      website
    )
  )

# Convert to sf object for mapgl
ski_resorts_sf <- ski_resorts %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = 4326)

# Create display table data - keep numeric values as numeric for filtering
ski_resorts_display <- ski_resorts %>%
  mutate(
    `Resort Name` = paste0('<a href="', website, '" target="_blank" style="color: #2563eb; text-decoration: none;">', name, '</a>'),
    #Location = paste0(city, ", ", state),
    State = case_when(
      state == "Pennsylvania" ~ "PA",
      state == "West Virginia" ~ "WV",
      state == "Virginia" ~ "VA",
      state == "Maryland" ~ "MD",
      TRUE ~ state
    ),
    `Drive Time` = drive_time_hours,
    `Pass Type` = pass_type,
    Trails = num_trails,
    Beginner = beginner_pct,
    Intermediate = intermediate_pct,
    Advanced = advanced_pct,
    `Terrain Park` = terrain_park,
    `Base Elev` = base_elevation,
    `Peak Elev` = peak_elevation,
    `Vertical Drop` = vertical_drop,
    Snowfall = avg_snowfall
  ) %>%
  select(
    `Resort Name`, State, `Drive Time`, `Pass Type`, Trails, 
    Beginner, Intermediate, Advanced, `Terrain Park`,
    `Base Elev`, `Peak Elev`, `Vertical Drop`, Snowfall
  )
```

```{r create-map}
#| column: page

# Create the base map with OpenFreeMap Liberty style
map <- mapgl::maplibre(
  center = c(-77.0369, 38.9072),
  zoom = 6.5,
  style = "https://tiles.openfreemap.org/styles/liberty"
)

# Create DC center point
dc_center <- st_point(c(-77.0369, 38.9072)) %>%
  st_sfc(crs = 4326) %>%
  st_sf()

# Transform to Web Mercator for accurate buffering at this latitude
# Using EPSG:3857 (Web Mercator) which works well for mid-latitudes
dc_projected <- st_transform(dc_center, crs = 3857)

# Create buffers - using more conservative estimates
# Accounting for mountainous terrain and winding roads: ~50mph average
# 2hr=100mi, 3hr=150mi, 4hr=200mi, 5hr=250mi
buffer_5hr <- st_buffer(dc_projected, dist = 250 * 1609.34) %>% st_transform(4326)
buffer_4hr <- st_buffer(dc_projected, dist = 200 * 1609.34) %>% st_transform(4326)
buffer_3hr <- st_buffer(dc_projected, dist = 150 * 1609.34) %>% st_transform(4326)
buffer_2hr <- st_buffer(dc_projected, dist = 100 * 1609.34) %>% st_transform(4326)

# Add drive time zones as fill layers (hidden by default - toggle via layer control)
map <- map %>%
  add_fill_layer(
    id = "drive_time_5hr",
    source = buffer_5hr,
    fill_color = "#FCA5A5",
    fill_opacity = 0.3,
    fill_outline_color = "#EF4444",
    visibility = "none"
  ) %>%
  add_fill_layer(
    id = "drive_time_4hr",
    source = buffer_4hr,
    fill_color = "#FDE047",
    fill_opacity = 0.3,
    fill_outline_color = "#EAB308",
    visibility = "none"
  ) %>%
  add_fill_layer(
    id = "drive_time_3hr",
    source = buffer_3hr,
    fill_color = "#A7F3D0",
    fill_opacity = 0.3,
    fill_outline_color = "#10B981",
    visibility = "none"
  ) %>%
  add_fill_layer(
    id = "drive_time_2hr",
    source = buffer_2hr,
    fill_color = "#93C5FD",
    fill_opacity = 0.3,
    fill_outline_color = "#3B82F6",
    visibility = "none"
  )

# Add resort markers on top
map <- map %>%
  add_circle_layer(
    id = "ski_resorts",
    source = ski_resorts_sf,
    circle_color = get_column("pass_color"),
    circle_radius = 8,
    circle_stroke_color = "white",
    circle_stroke_width = 2,
    popup = "popup_content",  # Column name as string
    tooltip = "name"           # Column name as string - this shows on hover!
  ) %>%
  add_navigation_control(position = "top-right") %>%
  add_layers_control(
    layers = c("drive_time_2hr", "drive_time_3hr", "drive_time_4hr", "drive_time_5hr"),
    position = "top-left"
  ) %>%
  add_categorical_legend(
    legend_title = "Pass Type",
    values = c("Epic Pass", "Ikon Pass", "Independent"),
    colors = c("#DC2626", "#0EA5E9", "#808080"),
    position = "bottom-left"
  )

map
```



## The data in one place

This may seem pretty small, but having these basic facts about the different resorts in a single location where they are searchable, sortable, and filterable is really convenient. I can quickly filter for all resorts within a 2 or 3 hour drive of DC and then see which kind of passes they take or compare their vertical drops or base/peak elevations, for example. Then, if I need more information I can click on the name of the resort in the table to view its website. I can also download the data if I want.

::: {.callout-tip}
## Table Features

- **Column Filters**: Click the filter icon in each column header to filter by specific criteria
- **Global Search**: Search across all columns using the search box at the top
- **Sort**: Click column headers to sort ascending/descending (default sorted by Drive Time)
- **Trail Difficulty Ratings**: Expand each row in the trails column to see the percentage of Beginner, Intermediate, and Advanced ski trails.
- **Color Coding**: 
  - Pass Type: Colored badges for Epic (Red), Ikon (Blue), Independent (Grey)
  - Data bars show relative number of trails (purple) and snowfall (blue)
  - Drive time color: Green (< 2hrs) | Yellow (2-3.5hrs) | Red (> 3.5hrs)
- **Pagination**: Choose how many resorts to view per page (5, 10, 16, 25, or 50)
:::

```{r create-table}
#| column: page

htmltools::tagList(
  reactable(
    ski_resorts_display,
    elementId = "ski-resorts-table",
    searchable = TRUE,
    filterable = TRUE,
    defaultPageSize = 5,
    showPageSizeOptions = TRUE,
    pageSizeOptions = c(5, 10, 16, 25, 50),
    defaultSorted = "Drive Time",
    compact = TRUE,
    theme = reactableTheme(
      borderColor = "#e5e7eb",
      stripedColor = "#f9fafb",
      highlightColor = "#eff6ff",
      cellPadding = "10px 12px",
      style = list(
        fontFamily = "-apple-system, BlinkMacSystemFont, 'Segoe UI', Roboto, sans-serif",
        fontSize = "14px"
      ),
      searchInputStyle = list(
        border = "1px solid #d1d5db",
        borderRadius = "6px",
        padding = "8px 12px",
        fontSize = "14px",
        width = "100%",
        maxWidth = "350px"
      ),
      headerStyle = list(
        background = "#f9fafb",
        color = "#374151",
        fontWeight = "600",
        fontSize = "12px",
        textTransform = "uppercase",
        letterSpacing = "0.5px",
        borderBottom = "2px solid #e5e7eb"
      )
    ),
    columns = list(
      `Resort Name` = colDef(
        html = TRUE,
        minWidth = 160,
        style = list(fontWeight = "500"),
        filterable = FALSE
      ),
      #Location = colDef(minWidth = 140),
      State = colDef(
        minWidth = 50,
        align = "center",
        style = list(color = "#6b7280", fontWeight = "600"),
        filterMethod = JS("function(rows, columnId, filterValue) {
          if (filterValue === 'all') return rows;
          return rows.filter(function(row) {
            return row.values[columnId] === filterValue;
          })
        }"),
        filterInput = function(values, name) {
          htmltools::tags$select(
            onchange = sprintf("Reactable.setFilter('ski-resorts-table', '%s', event.target.value)", name),
            style = "width: 100%; padding: 4px; border: 1px solid #d1d5db; border-radius: 4px; font-size: 13px;",
            htmltools::tags$option(value = "all", "All"),
            htmltools::tags$option(value = "MD", "MD"),
            htmltools::tags$option(value = "PA", "PA"),
            htmltools::tags$option(value = "VA", "VA"),
            htmltools::tags$option(value = "WV", "WV")
          )
        }
      ),
      `Drive Time` = colDef(
        name = "Drive (hrs)",
        minWidth = 50,
        align = "right",
        format = colFormat(digits = 1),
        filterMethod = JS("function(rows, columnId, filterValue) {
          return rows.filter(function(row) {
            var value = row.values[columnId];
            if (filterValue === 'all') return true;
            if (filterValue === 'under2') return value < 2;
            if (filterValue === '2to3') return value >= 2 && value <= 3;
            if (filterValue === '3to4') return value > 3 && value <= 4;
            if (filterValue === 'over4') return value > 4;
            return true;
          })
        }"),
        filterInput = function(values, name) {
          htmltools::tags$select(
            onchange = sprintf("Reactable.setFilter('ski-resorts-table', '%s', event.target.value)", name),
            style = "width: 100%; padding: 4px; border: 1px solid #d1d5db; border-radius: 4px; font-size: 13px;",
            htmltools::tags$option(value = "all", "All"),
            htmltools::tags$option(value = "under2", "< 2 hours"),
            htmltools::tags$option(value = "2to3", "2 - 3 hours"),
            htmltools::tags$option(value = "3to4", "3 - 4 hours"),
            htmltools::tags$option(value = "over4", "> 4 hours")
          )
        },
        style = function(value) {
          color <- if (value < 2) {
            "#dcfce7"
          } else if (value < 3.5) {
            "#fef9c3"
          } else {
            "#fee2e2"
          }
          list(
            background = color,
            fontWeight = "500",
            fontVariantNumeric = "tabular-nums"
          )
        }
      ),
      `Pass Type` = colDef(
        minWidth = 60,
        align = "center",
        filterMethod = JS("function(rows, columnId, filterValue) {
          if (filterValue === 'all') return rows;
          return rows.filter(function(row) {
            return row.values[columnId] === filterValue;
          })
        }"),
        filterInput = function(values, name) {
          htmltools::tags$select(
            onchange = sprintf("Reactable.setFilter('ski-resorts-table', '%s', event.target.value)", name),
            style = "width: 100%; padding: 4px; border: 1px solid #d1d5db; border-radius: 4px; font-size: 13px;",
            htmltools::tags$option(value = "all", "All"),
            htmltools::tags$option(value = "Epic", "Epic"),
            htmltools::tags$option(value = "Ikon", "Ikon"),
            htmltools::tags$option(value = "IND", "IND")
          )
        },
        cell = function(value) {
          color <- case_when(
            value == "Epic" ~ "#dc2626",
            value == "Ikon" ~ "#0284c7",
            TRUE ~ "#6b7280"
          )
          htmltools::span(
            style = list(
              fontWeight = "500",
              color = color
            ),
            value
          )
        }
      ),
      Trails = colDef(
        minWidth = 60,
        align = "center",
        format = colFormat(separators = TRUE),
        style = list(fontWeight = "500"),
        filterable = FALSE,
        details = function(index) {
          beginner <- ski_resorts_display[index, "Beginner"]
          intermediate <- ski_resorts_display[index, "Intermediate"]
          advanced <- ski_resorts_display[index, "Advanced"]
          htmltools::div(
            style = "padding: 12px; background: #f9fafb; border-top: 1px solid #e5e7eb;",
            htmltools::div(
              style = "display: grid; grid-template-columns: repeat(3, 1fr); gap: 16px;",
              htmltools::div(
                style = "text-align: center;",
                htmltools::div(style = "color: #16a34a; font-weight: 600; font-size: 18px;", paste0(beginner, "%")),
                htmltools::div(style = "color: #6b7280; font-size: 12px; text-transform: uppercase; margin-top: 4px;", "Beginner")
              ),
              htmltools::div(
                style = "text-align: center;",
                htmltools::div(style = "color: #2563eb; font-weight: 600; font-size: 18px;", paste0(intermediate, "%")),
                htmltools::div(style = "color: #6b7280; font-size: 12px; text-transform: uppercase; margin-top: 4px;", "Intermediate")
              ),
              htmltools::div(
                style = "text-align: center;",
                htmltools::div(style = "color: #000000; font-weight: 600; font-size: 18px;", paste0(advanced, "%")),
                htmltools::div(style = "color: #6b7280; font-size: 12px; text-transform: uppercase; margin-top: 4px;", "Advanced")
              )
            )
          )
        }
      ),
      Beginner = colDef(show = FALSE),
      Intermediate = colDef(show = FALSE),
      Advanced = colDef(show = FALSE),
      `Terrain Park` = colDef(
        minWidth = 70,
        align = "center",
        filterMethod = JS("function(rows, columnId, filterValue) {
          if (filterValue === 'all') return rows;
          return rows.filter(function(row) {
            return row.values[columnId] === filterValue;
          })
        }"),
        filterInput = function(values, name) {
          htmltools::tags$select(
            onchange = sprintf("Reactable.setFilter('ski-resorts-table', '%s', event.target.value)", name),
            style = "width: 100%; padding: 4px; border: 1px solid #d1d5db; border-radius: 4px; font-size: 13px;",
            htmltools::tags$option(value = "all", "All"),
            htmltools::tags$option(value = "Yes", "Yes"),
            htmltools::tags$option(value = "No", "No")
          )
        }
      ),
      `Base Elev` = colDef(
        name = "Base Elev (ft)",
        minWidth = 110,
        align = "right",
        format = colFormat(separators = TRUE),
        style = list(fontVariantNumeric = "tabular-nums"),
        filterMethod = JS("function(rows, columnId, filterValue) {
          return rows.filter(function(row) {
            return row.values[columnId] >= filterValue[0] && row.values[columnId] <= filterValue[1]
          })
        }"),
        filterInput = function(values, name) {
          htmltools::tags$div(
            style = "display: flex; gap: 4px; align-items: center;",
            htmltools::tags$input(
              type = "number",
              placeholder = "Min",
              style = "width: 60px; padding: 4px; border: 1px solid #d1d5db; border-radius: 4px; font-size: 12px;",
              oninput = sprintf("Reactable.setFilter('ski-resorts-table', '%s', [this.value || %s, this.parentElement.children[2].value || %s])", 
                               name, min(values, na.rm = TRUE), max(values, na.rm = TRUE))
            ),
            htmltools::tags$span("–", style = "font-size: 11px;"),
            htmltools::tags$input(
              type = "number",
              placeholder = "Max",
              style = "width: 60px; padding: 4px; border: 1px solid #d1d5db; border-radius: 4px; font-size: 12px;",
              oninput = sprintf("Reactable.setFilter('ski-resorts-table', '%s', [this.parentElement.children[0].value || %s, this.value || %s])", 
                               name, min(values, na.rm = TRUE), max(values, na.rm = TRUE))
            )
          )
        }
      ),
      `Peak Elev` = colDef(
        name = "Peak Elev (ft)",
        minWidth = 110,
        align = "right",
        format = colFormat(separators = TRUE),
        style = list(fontVariantNumeric = "tabular-nums"),
        filterMethod = JS("function(rows, columnId, filterValue) {
          return rows.filter(function(row) {
            return row.values[columnId] >= filterValue[0] && row.values[columnId] <= filterValue[1]
          })
        }"),
        filterInput = function(values, name) {
          htmltools::tags$div(
            style = "display: flex; gap: 4px; align-items: center;",
            htmltools::tags$input(
              type = "number",
              placeholder = "Min",
              style = "width: 60px; padding: 4px; border: 1px solid #d1d5db; border-radius: 4px; font-size: 12px;",
              oninput = sprintf("Reactable.setFilter('ski-resorts-table', '%s', [this.value || %s, this.parentElement.children[2].value || %s])", 
                               name, min(values, na.rm = TRUE), max(values, na.rm = TRUE))
            ),
            htmltools::tags$span("–", style = "font-size: 11px;"),
            htmltools::tags$input(
              type = "number",
              placeholder = "Max",
              style = "width: 60px; padding: 4px; border: 1px solid #d1d5db; border-radius: 4px; font-size: 12px;",
              oninput = sprintf("Reactable.setFilter('ski-resorts-table', '%s', [this.parentElement.children[0].value || %s, this.value || %s])", 
                               name, min(values, na.rm = TRUE), max(values, na.rm = TRUE))
            )
          )
        }
      ),
      `Vertical Drop` = colDef(
        name = "Vertical (ft)",
        minWidth = 100,
        align = "right",
        format = colFormat(separators = TRUE),
        style = list(fontVariantNumeric = "tabular-nums", fontWeight = "500"),
        filterMethod = JS("function(rows, columnId, filterValue) {
          return rows.filter(function(row) {
            return row.values[columnId] >= filterValue[0] && row.values[columnId] <= filterValue[1]
          })
        }"),
        filterInput = function(values, name) {
          htmltools::tags$div(
            style = "display: flex; gap: 4px; align-items: center;",
            htmltools::tags$input(
              type = "number",
              placeholder = "Min",
              style = "width: 60px; padding: 4px; border: 1px solid #d1d5db; border-radius: 4px; font-size: 12px;",
              oninput = sprintf("Reactable.setFilter('ski-resorts-table', '%s', [this.value || %s, this.parentElement.children[2].value || %s])", 
                               name, min(values, na.rm = TRUE), max(values, na.rm = TRUE))
            ),
            htmltools::tags$span("–", style = "font-size: 11px;"),
            htmltools::tags$input(
              type = "number",
              placeholder = "Max",
              style = "width: 60px; padding: 4px; border: 1px solid #d1d5db; border-radius: 4px; font-size: 12px;",
              oninput = sprintf("Reactable.setFilter('ski-resorts-table', '%s', [this.parentElement.children[0].value || %s, this.value || %s])", 
                               name, min(values, na.rm = TRUE), max(values, na.rm = TRUE))
            )
          )
        }
      ),
      Snowfall = colDef(
        name = "Snow (in/yr)",
        minWidth = 100,
        align = "right",
        format = colFormat(suffix = '"'),
        style = list(fontVariantNumeric = "tabular-nums"),
        filterMethod = JS("function(rows, columnId, filterValue) {
          return rows.filter(function(row) {
            return row.values[columnId] >= filterValue[0] && row.values[columnId] <= filterValue[1]
          })
        }"),
        filterInput = function(values, name) {
          htmltools::tags$div(
            style = "display: flex; gap: 4px; align-items: center;",
            htmltools::tags$input(
              type = "number",
              placeholder = "Min",
              style = "width: 50px; padding: 4px; border: 1px solid #d1d5db; border-radius: 4px; font-size: 12px;",
              oninput = sprintf("Reactable.setFilter('ski-resorts-table', '%s', [this.value || %s, this.parentElement.children[2].value || %s])", 
                               name, min(values, na.rm = TRUE), max(values, na.rm = TRUE))
            ),
            htmltools::tags$span("–", style = "font-size: 11px;"),
            htmltools::tags$input(
              type = "number",
              placeholder = "Max",
              style = "width: 50px; padding: 4px; border: 1px solid #d1d5db; border-radius: 4px; font-size: 12px;",
              oninput = sprintf("Reactable.setFilter('ski-resorts-table', '%s', [this.parentElement.children[0].value || %s, this.value || %s])", 
                               name, min(values, na.rm = TRUE), max(values, na.rm = TRUE))
            )
          )
        }
      )
    )
  ),
htmltools::div(
  style = "margin-top: 15px; text-align: right;",
  htmltools::tags$button(
    onclick = "Reactable.downloadDataCSV('ski-resorts-table', 'dc_ski_resorts.csv')",
    style = "background: linear-gradient(135deg, #667eea 0%, #764ba2 100%); color: white; border: none; border-radius: 6px; padding: 10px 20px; font-weight: 600; font-size: 14px; cursor: pointer; transition: all 0.2s ease;",
    onmouseover = "this.style.transform='translateY(-2px)'; this.style.boxShadow='0 4px 12px rgba(102, 126, 234, 0.4)';",
    onmouseout = "this.style.transform='translateY(0)'; this.style.boxShadow='none';",
    "📥 Download Data (CSV)"
  )
)
)

```


---

**Data Sources:** Official resort websites, OnTheSnow.com, DCSki.com, SkiCentral.com  
**Last Updated:** February 2026  
**Map Engine:** MapLibre GL with OpenFreeMap Liberty style
