---
title: "Ski the DMV"
format: 
  html:
    page-layout: article
    toc: true
    toc-location: left
execute:
    echo: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

# Your Complete Guide to DC Area Skiing

::: {.callout-note icon="false" appearance="simple"}
## 📊 Quick Stats

**16 Resorts** \| **5 States** \| **\< 5 Hours Drive** \| **Epic, Ikon & Independent Passes**
:::

## Why This Guide Exists

If you're like me, you love skiing and want a **simple, searchable resource** to find the perfect resort near Washington, DC. Sure, there are websites that describe individual resorts, but finding one comprehensive table where you can search, filter, and compare? That's harder to come by so I built it myself.

### What Makes This Different

✅ **All-in-One Table** – Search and filter 16 resorts by location, pass type, difficulty, and drive time\
✅ **Pass Type Info** – Quickly see which resorts accept Epic, Ikon, or Independent passes (no more checking individual websites!)\
✅ **Interactive Map** – Visual drive time zones show you what's reachable in 2, 3, 4, or 5 hours\
✅ **Detailed Stats** – Trail counts, vertical drop, snowfall averages, and terrain breakdowns

::: {.callout-tip icon="false"}
## 🎯 Pro Tip

New to skiing? Start with resorts under 2 hours away (use the Drive Time filter in the table below). Whitetail, Liberty, and Bryce are all great beginner-friendly options within easy reach.
:::

------------------------------------------------------------------------

# 🗺️ Interactive Map: Where Can You Ski?

Explore all 16 ski resorts within a 5-hour drive of Washington, DC. **Hover over markers** to see resort names, **click for details**, and **toggle drive time zones** to see what's reachable in your time budget.

::: {.callout-note icon="false"}
## 🧭 How to Use the Map

-   **Hover** over any marker to see the resort name
-   **Click** a marker to open a popup with resort details and a website link
-   **Toggle layers** (📋 icon, top-left) to show/hide 2, 3, 4, and 5-hour drive zones
-   **Zoom & pan** to explore the region
-   **Marker colors**: [**Red** = Epic Pass]{style="color:#DC2626"} \| [**Blue** = Ikon Pass]{style="color:#0EA5E9"} \| [**Grey** = Independent]{style="color:#808080"}

*Note: Drive time zones show straight-line distances (\~50mph average for mountainous roads). Actual drive times vary by traffic and road conditions.*
:::

```{r load-libraries}
library(tidyverse)
library(mapgl)
library(reactable)
library(reactablefmtr)
library(htmltools)
library(htmlwidgets)
library(sf)
```

```{r create-data}
#Compiled data on mid-Atlantic ski resorts within a 5 hour drive of Washington, DC
ski_resorts <- readxl::read_xlsx("ski_resort_data.xlsx") |> 
  mutate(
     # Convert float columns to integers
    beginner_pct = as.integer(beginner_pct),
    intermediate_pct = as.integer(intermediate_pct),
    advanced_pct = as.integer(advanced_pct),
    num_trails = as.integer(num_trails),
    terrain_acres = as.integer(terrain_acres),
    base_elevation = as.integer(base_elevation),
    peak_elevation = as.integer(peak_elevation),
    avg_snowfall = as.integer(avg_snowfall),
    vertical_drop = as.integer(vertical_drop),
    image_url = ifelse(
      !grepl("^https?://", image_url),  # If not already a full URL
      paste0("./", image_url),            # Add ./ prefix for relative path
      image_url)               
  )

# Determine pass type color for each resort
ski_resorts <- ski_resorts %>%
  mutate(
    pass_color = case_when(
      pass_type == "Epic" ~ "#DC2626",
      pass_type == "Ikon" ~ "#0EA5E9",
      TRUE ~ "#808080"  # Grey for Independent
    ),
    # Create popup HTML for each resort
    popup_content = sprintf('
<div style="font-family: Arial, sans-serif; min-width: 220px; max-width: 260px;">
  <div style="display: flex; align-items: center; margin-bottom: 8px; padding-bottom: 6px; border-bottom: 2px solid #3b82f6;">
    <img src="%s" alt="%s" style="height: 24px; width: auto; margin-right: 8px; object-fit: contain;">
    <h3 style="margin: 0; color: #1e40af; font-size: 14px; font-weight: bold;">%s</h3>
  </div>
  <table style="width: 100%%; border-collapse: collapse; font-size: 11px;">
    <tr style="background-color: #f3f4f6;">
      <td style="padding: 4px; font-weight: bold; border: 1px solid #e5e7eb; width: 38%%;">Location</td>
      <td style="padding: 4px; border: 1px solid #e5e7eb;">%s, %s</td>
    </tr>
    <tr>
      <td style="padding: 4px; font-weight: bold; border: 1px solid #e5e7eb;">Pass</td>
      <td style="padding: 4px; border: 1px solid #e5e7eb;"><strong style="color: %s;">%s</strong></td>
    </tr>
    <tr style="background-color: #f3f4f6;">
      <td style="padding: 4px; font-weight: bold; border: 1px solid #e5e7eb;">Trails</td>
      <td style="padding: 4px; border: 1px solid #e5e7eb;">%d on %d acres</td>
    </tr>
    <tr>
      <td style="padding: 4px; font-weight: bold; border: 1px solid #e5e7eb;">Terrain Park</td>
      <td style="padding: 4px; border: 1px solid #e5e7eb;">%s</td>
    </tr>
    <tr style="background-color: #f3f4f6;">
      <td style="padding: 4px; font-weight: bold; border: 1px solid #e5e7eb;">Difficulty</td>
      <td style="padding: 4px; border: 1px solid #e5e7eb;">
        <span style="color: #22c55e;">●</span>%d%% <span style="color: #3b82f6;">■</span>%d%% <span style="color: #000;">◆</span>%d%%
      </td>
    </tr>
    <tr>
      <td style="padding: 4px; font-weight: bold; border: 1px solid #e5e7eb;">Elevations</td>
      <td style="padding: 4px; border: 1px solid #e5e7eb;">
        Base: %s ft. | Peak: %s ft. | Drop: %s ft.
      </td>
    </tr>
    <tr style="background-color: #f3f4f6;">
      <td style="padding: 4px; font-weight: bold; border: 1px solid #e5e7eb;">Snow</td>
      <td style="padding: 4px; border: 1px solid #e5e7eb;">%d in/yr</td>
    </tr>
    <tr>
      <td style="padding: 4px; font-weight: bold; border: 1px solid #e5e7eb;">Drive</td>
      <td style="padding: 4px; border: 1px solid #e5e7eb;">%.1f hrs</td>
    </tr>
    <tr style="background-color: #f3f4f6;">
      <td colspan="2" style="padding: 5px; text-align: center; border: 1px solid #e5e7eb;">
        <a href="%s" target="_blank" style="color: #2563eb; text-decoration: none; font-weight: bold; font-size: 10px;">
          🌐 Website
        </a>
      </td>
    </tr>
  </table>
</div>',
      image_url, name, name,
      city, state,
      pass_color, pass_type,
      num_trails, terrain_acres,
      terrain_park,
      beginner_pct, intermediate_pct, advanced_pct, 
      format(base_elevation, big.mark = ","),
      format(peak_elevation, big.mark = ","),
      format(vertical_drop, big.mark = ","),
      avg_snowfall,
      drive_time_hours,
      website
    )
  )

# Convert to sf object for mapgl
ski_resorts_sf <- ski_resorts %>%
  st_as_sf(coords = c("longitude", "latitude"), crs = 4326)

# Create display table data - keep numeric values as numeric for filtering
ski_resorts_display <- ski_resorts %>%
  mutate(
    `Resort Name` = paste0('<a href="', website, '" target="_blank" style="color: #2563eb; text-decoration: none;">', name, '</a>'),
    #Location = paste0(city, ", ", state),
    State = case_when(
      state == "Pennsylvania" ~ "PA",
      state == "West Virginia" ~ "WV",
      state == "Virginia" ~ "VA",
      state == "Maryland" ~ "MD",
      TRUE ~ state
    ),
    `Drive Time` = drive_time_hours,
    `Pass Type` = pass_type,
    Trails = num_trails,
    Beginner = beginner_pct,
    Intermediate = intermediate_pct,
    Advanced = advanced_pct,
    `Terrain Park` = terrain_park,
    `Base Elev` = base_elevation,
    `Peak Elev` = peak_elevation,
    `Vertical Drop` = vertical_drop,
    Snowfall = avg_snowfall
  ) %>%
  select(
    `Resort Name`, State, `Drive Time`, `Pass Type`, Trails, 
    Beginner, Intermediate, Advanced, `Terrain Park`,
    `Base Elev`, `Peak Elev`, `Vertical Drop`, Snowfall
  )
```

```{r create-map}
#| column: page

# Create the base map with OpenFreeMap Liberty style
map <- mapgl::maplibre(
  center = c(-77.0369, 38.9072),
  zoom = 5.5,
  style = "https://tiles.openfreemap.org/styles/liberty"
)

# Create DC center point
dc_center <- st_point(c(-77.0369, 38.9072)) %>%
  st_sfc(crs = 4326) %>%
  st_sf()

# Transform to Web Mercator for accurate buffering at this latitude
# Using EPSG:3857 (Web Mercator) which works well for mid-latitudes
dc_projected <- st_transform(dc_center, crs = 3857)

# Create buffers - using more conservative estimates
# Accounting for mountainous terrain and winding roads: ~50mph average
# 2hr=100mi, 3hr=150mi, 4hr=200mi, 5hr=250mi
buffer_5hr <- st_buffer(dc_projected, dist = 250 * 1609.34) %>% st_transform(4326)
buffer_4hr <- st_buffer(dc_projected, dist = 200 * 1609.34) %>% st_transform(4326)
buffer_3hr <- st_buffer(dc_projected, dist = 150 * 1609.34) %>% st_transform(4326)
buffer_2hr <- st_buffer(dc_projected, dist = 100 * 1609.34) %>% st_transform(4326)

# Add drive time zones as fill layers (hidden by default - toggle via layer control)
map <- map %>%
  add_fill_layer(
    id = "drive_time_5hr",
    source = buffer_5hr,
    fill_color = "#FCA5A5",
    fill_opacity = 0.3,
    fill_outline_color = "#EF4444",
    visibility = "none"
  ) %>%
  add_fill_layer(
    id = "drive_time_4hr",
    source = buffer_4hr,
    fill_color = "#FDE047",
    fill_opacity = 0.3,
    fill_outline_color = "#EAB308",
    visibility = "none"
  ) %>%
  add_fill_layer(
    id = "drive_time_3hr",
    source = buffer_3hr,
    fill_color = "#A7F3D0",
    fill_opacity = 0.3,
    fill_outline_color = "#10B981",
    visibility = "none"
  ) %>%
  add_fill_layer(
    id = "drive_time_2hr",
    source = buffer_2hr,
    fill_color = "#93C5FD",
    fill_opacity = 0.3,
    fill_outline_color = "#3B82F6",
    visibility = "none"
  )

# Add resort markers on top
map <- map %>%
  add_circle_layer(
    id = "ski_resorts",
    source = ski_resorts_sf,
    circle_color = get_column("pass_color"),
    circle_radius = 8,
    circle_stroke_color = "white",
    circle_stroke_width = 2,
    popup = "popup_content",  # Column name as string
    tooltip = "name"           # Column name as string - this shows on hover!
  ) %>%
  add_navigation_control(position = "top-right") %>%
  add_layers_control(
    layers = c("drive_time_2hr", "drive_time_3hr", "drive_time_4hr", "drive_time_5hr"),
    position = "top-left"
  ) %>%
  add_categorical_legend(
    legend_title = "Pass Type",
    values = c("Epic Pass", "Ikon Pass", "Independent"),
    colors = c("#DC2626", "#0EA5E9", "#808080"),
    position = "bottom-left"
  )

map
```

------------------------------------------------------------------------

# 📋 Complete Resort Data Table

Stop juggling multiple tabs! This searchable, filterable table puts all the essential resort information in one place. **Compare vertical drops, filter by pass type, check drive times** – all without leaving this page.

### Why This Table is Useful

-   **Quick Comparisons** – See at a glance which resorts have the most trails, best snowfall, or biggest vertical drops
-   **Smart Filtering** – Filter by state, pass type, terrain park availability, or drive time with easy dropdown menus
-   **Pass Planning** – Instantly identify which resorts work with your Epic or Ikon pass
-   **One-Click Details** – Click any resort name to visit their official website
-   **Download Option** – Export the data for your own analysis

::: {.callout-tip icon="false"}
## 💡 Quick Filtering Tips

**Looking for a weekend trip?** Filter Drive Time to "\< 2 hours" → See which are closest\
**Have an Epic Pass?** Filter Pass Type to "Epic" → See all your options\
**Want big terrain?** Click the "Vertical (ft)" column header to sort by biggest drops\
**Beginner-friendly?** Expand the Trails column to see difficulty breakdowns
:::

```{r create-table}
#| column: page

htmltools::tagList(
  reactable(
    ski_resorts_display,
    elementId = "ski-resorts-table",
    searchable = TRUE,
    filterable = TRUE,
    defaultPageSize = 16,
    showPageSizeOptions = TRUE,
    pageSizeOptions = c(5, 10, 16, 25, 50),
    defaultSorted = "Drive Time",
    compact = TRUE,
    theme = reactableTheme(
      borderColor = "#e5e7eb",
      stripedColor = "#f9fafb",
      highlightColor = "#eff6ff",
      cellPadding = "10px 12px",
      style = list(
        fontFamily = "-apple-system, BlinkMacSystemFont, 'Segoe UI', Roboto, sans-serif",
        fontSize = "14px"
      ),
      searchInputStyle = list(
        border = "1px solid #d1d5db",
        borderRadius = "6px",
        padding = "8px 12px",
        fontSize = "14px",
        width = "100%",
        maxWidth = "350px"
      ),
      headerStyle = list(
        background = "#f9fafb",
        color = "#374151",
        fontWeight = "600",
        fontSize = "12px",
        textTransform = "uppercase",
        letterSpacing = "0.5px",
        borderBottom = "2px solid #e5e7eb"
      )
    ),
    columns = list(
      `Resort Name` = colDef(
        html = TRUE,
        minWidth = 160,
        style = list(fontWeight = "500"),
        filterable = FALSE
      ),
      #Location = colDef(minWidth = 140),
      State = colDef(
        minWidth = 50,
        align = "center",
        style = list(color = "#6b7280", fontWeight = "600"),
        filterMethod = JS("function(rows, columnId, filterValue) {
          if (filterValue === 'all') return rows;
          return rows.filter(function(row) {
            return row.values[columnId] === filterValue;
          })
        }"),
        filterInput = function(values, name) {
          htmltools::tags$select(
            onchange = sprintf("Reactable.setFilter('ski-resorts-table', '%s', event.target.value)", name),
            style = "width: 100%; padding: 4px; border: 1px solid #d1d5db; border-radius: 4px; font-size: 13px;",
            htmltools::tags$option(value = "all", "All"),
            htmltools::tags$option(value = "MD", "MD"),
            htmltools::tags$option(value = "PA", "PA"),
            htmltools::tags$option(value = "VA", "VA"),
            htmltools::tags$option(value = "WV", "WV")
          )
        }
      ),
      `Drive Time` = colDef(
        name = "Drive (hrs)",
        minWidth = 50,
        align = "right",
        format = colFormat(digits = 1),
        filterMethod = JS("function(rows, columnId, filterValue) {
          return rows.filter(function(row) {
            var value = row.values[columnId];
            if (filterValue === 'all') return true;
            if (filterValue === 'under2') return value < 2;
            if (filterValue === '2to3') return value >= 2 && value <= 3;
            if (filterValue === '3to4') return value > 3 && value <= 4;
            if (filterValue === 'over4') return value > 4;
            return true;
          })
        }"),
        filterInput = function(values, name) {
          htmltools::tags$select(
            onchange = sprintf("Reactable.setFilter('ski-resorts-table', '%s', event.target.value)", name),
            style = "width: 100%; padding: 4px; border: 1px solid #d1d5db; border-radius: 4px; font-size: 13px;",
            htmltools::tags$option(value = "all", "All"),
            htmltools::tags$option(value = "under2", "< 2 hours"),
            htmltools::tags$option(value = "2to3", "2 - 3 hours"),
            htmltools::tags$option(value = "3to4", "3 - 4 hours"),
            htmltools::tags$option(value = "over4", "> 4 hours")
          )
        },
        style = function(value) {
          color <- if (value < 2) {
            "#dcfce7"
          } else if (value < 3.5) {
            "#fef9c3"
          } else {
            "#fee2e2"
          }
          list(
            background = color,
            fontWeight = "500",
            fontVariantNumeric = "tabular-nums"
          )
        }
      ),
      `Pass Type` = colDef(
        minWidth = 60,
        align = "center",
        filterMethod = JS("function(rows, columnId, filterValue) {
          if (filterValue === 'all') return rows;
          return rows.filter(function(row) {
            return row.values[columnId] === filterValue;
          })
        }"),
        filterInput = function(values, name) {
          htmltools::tags$select(
            onchange = sprintf("Reactable.setFilter('ski-resorts-table', '%s', event.target.value)", name),
            style = "width: 100%; padding: 4px; border: 1px solid #d1d5db; border-radius: 4px; font-size: 13px;",
            htmltools::tags$option(value = "all", "All"),
            htmltools::tags$option(value = "Epic", "Epic"),
            htmltools::tags$option(value = "Ikon", "Ikon"),
            htmltools::tags$option(value = "IND", "IND")
          )
        },
        cell = function(value) {
          color <- case_when(
            value == "Epic" ~ "#dc2626",
            value == "Ikon" ~ "#0284c7",
            TRUE ~ "#6b7280"
          )
          htmltools::span(
            style = list(
              fontWeight = "500",
              color = color
            ),
            value
          )
        }
      ),
      Trails = colDef(
        minWidth = 60,
        align = "center",
        format = colFormat(separators = TRUE),
        style = list(fontWeight = "500"),
        filterable = FALSE,
        details = function(index) {
          beginner <- ski_resorts_display[index, "Beginner"]
          intermediate <- ski_resorts_display[index, "Intermediate"]
          advanced <- ski_resorts_display[index, "Advanced"]
          htmltools::div(
            style = "padding: 12px; background: #f9fafb; border-top: 1px solid #e5e7eb;",
            htmltools::div(
              style = "display: grid; grid-template-columns: repeat(3, 1fr); gap: 16px;",
              htmltools::div(
                style = "text-align: center;",
                htmltools::div(style = "color: #16a34a; font-weight: 600; font-size: 18px;", paste0(beginner, "%")),
                htmltools::div(style = "color: #6b7280; font-size: 12px; text-transform: uppercase; margin-top: 4px;", "Beginner")
              ),
              htmltools::div(
                style = "text-align: center;",
                htmltools::div(style = "color: #2563eb; font-weight: 600; font-size: 18px;", paste0(intermediate, "%")),
                htmltools::div(style = "color: #6b7280; font-size: 12px; text-transform: uppercase; margin-top: 4px;", "Intermediate")
              ),
              htmltools::div(
                style = "text-align: center;",
                htmltools::div(style = "color: #000000; font-weight: 600; font-size: 18px;", paste0(advanced, "%")),
                htmltools::div(style = "color: #6b7280; font-size: 12px; text-transform: uppercase; margin-top: 4px;", "Advanced")
              )
            )
          )
        }
      ),
      Beginner = colDef(show = FALSE),
      Intermediate = colDef(show = FALSE),
      Advanced = colDef(show = FALSE),
      `Terrain Park` = colDef(
        minWidth = 70,
        align = "center",
        filterMethod = JS("function(rows, columnId, filterValue) {
          if (filterValue === 'all') return rows;
          return rows.filter(function(row) {
            return row.values[columnId] === filterValue;
          })
        }"),
        filterInput = function(values, name) {
          htmltools::tags$select(
            onchange = sprintf("Reactable.setFilter('ski-resorts-table', '%s', event.target.value)", name),
            style = "width: 100%; padding: 4px; border: 1px solid #d1d5db; border-radius: 4px; font-size: 13px;",
            htmltools::tags$option(value = "all", "All"),
            htmltools::tags$option(value = "Yes", "Yes"),
            htmltools::tags$option(value = "No", "No")
          )
        }
      ),
      `Base Elev` = colDef(
        name = "Base Elev (ft)",
        minWidth = 110,
        align = "right",
        format = colFormat(separators = TRUE),
        style = list(fontVariantNumeric = "tabular-nums"),
        filterMethod = JS("function(rows, columnId, filterValue) {
          return rows.filter(function(row) {
            return row.values[columnId] >= filterValue[0] && row.values[columnId] <= filterValue[1]
          })
        }"),
        filterInput = function(values, name) {
          htmltools::tags$div(
            style = "display: flex; gap: 4px; align-items: center;",
            htmltools::tags$input(
              type = "number",
              placeholder = "Min",
              style = "width: 60px; padding: 4px; border: 1px solid #d1d5db; border-radius: 4px; font-size: 12px;",
              oninput = sprintf("Reactable.setFilter('ski-resorts-table', '%s', [this.value || %s, this.parentElement.children[2].value || %s])", 
                               name, min(values, na.rm = TRUE), max(values, na.rm = TRUE))
            ),
            htmltools::tags$span("–", style = "font-size: 11px;"),
            htmltools::tags$input(
              type = "number",
              placeholder = "Max",
              style = "width: 60px; padding: 4px; border: 1px solid #d1d5db; border-radius: 4px; font-size: 12px;",
              oninput = sprintf("Reactable.setFilter('ski-resorts-table', '%s', [this.parentElement.children[0].value || %s, this.value || %s])", 
                               name, min(values, na.rm = TRUE), max(values, na.rm = TRUE))
            )
          )
        }
      ),
      `Peak Elev` = colDef(
        name = "Peak Elev (ft)",
        minWidth = 110,
        align = "right",
        format = colFormat(separators = TRUE),
        style = list(fontVariantNumeric = "tabular-nums"),
        filterMethod = JS("function(rows, columnId, filterValue) {
          return rows.filter(function(row) {
            return row.values[columnId] >= filterValue[0] && row.values[columnId] <= filterValue[1]
          })
        }"),
        filterInput = function(values, name) {
          htmltools::tags$div(
            style = "display: flex; gap: 4px; align-items: center;",
            htmltools::tags$input(
              type = "number",
              placeholder = "Min",
              style = "width: 60px; padding: 4px; border: 1px solid #d1d5db; border-radius: 4px; font-size: 12px;",
              oninput = sprintf("Reactable.setFilter('ski-resorts-table', '%s', [this.value || %s, this.parentElement.children[2].value || %s])", 
                               name, min(values, na.rm = TRUE), max(values, na.rm = TRUE))
            ),
            htmltools::tags$span("–", style = "font-size: 11px;"),
            htmltools::tags$input(
              type = "number",
              placeholder = "Max",
              style = "width: 60px; padding: 4px; border: 1px solid #d1d5db; border-radius: 4px; font-size: 12px;",
              oninput = sprintf("Reactable.setFilter('ski-resorts-table', '%s', [this.parentElement.children[0].value || %s, this.value || %s])", 
                               name, min(values, na.rm = TRUE), max(values, na.rm = TRUE))
            )
          )
        }
      ),
      `Vertical Drop` = colDef(
        name = "Vertical (ft)",
        minWidth = 100,
        align = "right",
        format = colFormat(separators = TRUE),
        style = list(fontVariantNumeric = "tabular-nums", fontWeight = "500"),
        filterMethod = JS("function(rows, columnId, filterValue) {
          return rows.filter(function(row) {
            return row.values[columnId] >= filterValue[0] && row.values[columnId] <= filterValue[1]
          })
        }"),
        filterInput = function(values, name) {
          htmltools::tags$div(
            style = "display: flex; gap: 4px; align-items: center;",
            htmltools::tags$input(
              type = "number",
              placeholder = "Min",
              style = "width: 60px; padding: 4px; border: 1px solid #d1d5db; border-radius: 4px; font-size: 12px;",
              oninput = sprintf("Reactable.setFilter('ski-resorts-table', '%s', [this.value || %s, this.parentElement.children[2].value || %s])", 
                               name, min(values, na.rm = TRUE), max(values, na.rm = TRUE))
            ),
            htmltools::tags$span("–", style = "font-size: 11px;"),
            htmltools::tags$input(
              type = "number",
              placeholder = "Max",
              style = "width: 60px; padding: 4px; border: 1px solid #d1d5db; border-radius: 4px; font-size: 12px;",
              oninput = sprintf("Reactable.setFilter('ski-resorts-table', '%s', [this.parentElement.children[0].value || %s, this.value || %s])", 
                               name, min(values, na.rm = TRUE), max(values, na.rm = TRUE))
            )
          )
        }
      ),
      Snowfall = colDef(
        name = "Snow (in/yr)",
        minWidth = 100,
        align = "right",
        format = colFormat(suffix = '"'),
        style = list(fontVariantNumeric = "tabular-nums"),
        filterMethod = JS("function(rows, columnId, filterValue) {
          return rows.filter(function(row) {
            return row.values[columnId] >= filterValue[0] && row.values[columnId] <= filterValue[1]
          })
        }"),
        filterInput = function(values, name) {
          htmltools::tags$div(
            style = "display: flex; gap: 4px; align-items: center;",
            htmltools::tags$input(
              type = "number",
              placeholder = "Min",
              style = "width: 50px; padding: 4px; border: 1px solid #d1d5db; border-radius: 4px; font-size: 12px;",
              oninput = sprintf("Reactable.setFilter('ski-resorts-table', '%s', [this.value || %s, this.parentElement.children[2].value || %s])", 
                               name, min(values, na.rm = TRUE), max(values, na.rm = TRUE))
            ),
            htmltools::tags$span("–", style = "font-size: 11px;"),
            htmltools::tags$input(
              type = "number",
              placeholder = "Max",
              style = "width: 50px; padding: 4px; border: 1px solid #d1d5db; border-radius: 4px; font-size: 12px;",
              oninput = sprintf("Reactable.setFilter('ski-resorts-table', '%s', [this.parentElement.children[0].value || %s, this.value || %s])", 
                               name, min(values, na.rm = TRUE), max(values, na.rm = TRUE))
            )
          )
        }
      )
    )
  ),
htmltools::div(
  style = "margin-top: 15px; text-align: right;",
  htmltools::tags$button(
    onclick = "Reactable.downloadDataCSV('ski-resorts-table', 'dc_ski_resorts.csv')",
    style = "background: linear-gradient(135deg, #667eea 0%, #764ba2 100%); color: white; border: none; border-radius: 6px; padding: 10px 20px; font-weight: 600; font-size: 14px; cursor: pointer; transition: all 0.2s ease;",
    onmouseover = "this.style.transform='translateY(-2px)'; this.style.boxShadow='0 4px 12px rgba(102, 126, 234, 0.4)';",
    onmouseout = "this.style.transform='translateY(0)'; this.style.boxShadow='none';",
    "📥 Download Data (CSV)"
  )
)
)

```

------------------------------------------------------------------------

**Data Sources:** Official resort websites, OnTheSnow.com, DCSki.com, SkiCentral.com\
**Last Updated:** February 2026\
**Map Engine:** MapLibre GL with OpenFreeMap Liberty style